SPARQL on the Open, Decentralised Web

### 2016-06-23 dissertation/introduction.tex
hypermedia

>>>>

However, in terms of utility when programming, advanced query
languages such as SPARQL may not be needed for many applications, and
may represent an overly high barrier to entry.

Hypermedia is the idea that all information needed to drive
interaction in an application must be readily available in the
request-response dialogue. For human interactions, this has been
understood as a requirement for a long time, one has to tell the user
how to interact with the application, if not, the user is unlikely to
be able to solve the task. Contemporary efforts now extend this to
machine-machine interactions.

In this context, hypermedia types is a way to classify what kind of
operations a certain media type can help the application perform.
